---
title: "Employee Dataset Question"
output: html_notebook
---

You are required to write the appropriate R commands statements to read the file in data frame 'dsalary' and answer the following:

| Rank     | YrsSincePhd | YrsService | Gender | Salary(K) |
|----------|-------------|------------|--------|-----------|
| AstProf  | 3           | 7          | M      | 85        |
| AstProf  | 8           | 12         | F      | 95        |
| AstProf  | 2           | 5          | F      | 80        |
| AsctProf | 9           | 18         | M      | 150       |
| AsctProf | 10          | 19         | F      | 150       |
| AsctProf | 10          | 18         | M      | 160       |
| Prof     | 20          | 25         | M      | 200       |
| Prof     | 22          | 29         | F      | 250       |
| Prof     | 20          | 25         | M      | 210       |
| Prof     | 22          | 29         | F      | 220       |

```{r}
dsalary=read.csv('E:/Data Science/Dataset/Employee.csv',sep=" ")
print(dsalary)
```

a)  Find out the number of observations and variables in the given dataset.

    ```{r}
    print(paste("Observations:",nrow(dsalary)))
    print(paste("Variables:",ncol(dsalary)))
    ```

b)  Calculate the average salary of all faculty members, male and female faculty members separately, and rank wise faculty members.

    ```{r}
    print(paste("Average salary of all faculty members: ",mean(dsalary$Salary.K.)))
    print(paste("Average salary of male members: ",mean(dsalary[which(dsalary$Gender=='M'),]$Salary.K.)))
    print(paste("Average salary of Female members: ",mean(dsalary[which(dsalary$Gender=='F'),]$Salary.K.)))

    ```

c)  Count the number of male Asst. Prof and female Associate professors.

    ```{r}
    d=which((dsalary$Gender=="M") & (dsalary$Rank=="AsctProf"))
    print(length(d))
    ```

d)  Display first two columns of second row.

    ```{r}
    print(dsalary[2,1:2])
    ```

e)  Display YrsSincePhd and Yrsof Service of all the teachers.

    ```{r}
    print(dsalary[[2,3]])
    ```

f)  Print the highest salary drawing male Associate Professor with maximum year of services.\

g)  Display the Rank of the teacher whose salary is more than 150.\

h)  Add a new column 'special allowance' which is 5% of the salary.\

i)  Increase the salary of male prof by 5% and female prof by 10% and then compare the average salary between these two.\

j)  Create a vector which contains the average salary of each rank.

```{r}
print("Vector which contains the average salary of each rank")
avg_sal=c(aggregate(Salary~Rank,dsalary,mean))
print(avg_sal)
```
